Updates on the Exoplanet Orbit Database

### 2014-02-26 draft/ms.tex
First draft of introduction.

% The business of tracking planet discoveries
As the number of exoplanet discoveries keeps rising, it is important
to keep tracking these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

% A brief history of EOD

According to Google Analytics, $47,000$ people visited exoplanets.org
in 2013.

What this paper is about: an update on EOD and the services our
website, exoplanets.org, provide.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}

>>>>

% The business of tracking planet discoveries
As the number of exoplanet discoveries keeps rising, it is important
to keep tracking these discoveries and cataloging the orbital
parameters and host star properties of exoplanet systems. There are
several entities that are devoted to this effort, including the
Exoplanet Orbit Database (EOD) and Exoplanets Data Explorer\footnote{See
  \url{http://exoplanets.org}.} \citep{Wright2011}, the Extrasolar
Planets Encyclopaedia\footnote{See \url{http://exoplanet.eu}.}
\citep{Schneider2011}, the NASA Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}, and so on.

% What is this paper about
This paper describes the continuing efforts since \cite{Wright2011} to
maintain the EOD and the Exoplanets Data Explorer at
exoplanets.org. The EOD has expanded to include all robustly-detected
exoplanets (around {\it any} type of host star) with well-determined
orbital parameters published in peer-reviewed literature. It has also
ingested more parameters of the exoplanet systems and host stars, and
some parameters are revised or deleted. We describe the updates with
the EOD in Section~\ref{sec:update}.

% also the website
We also describe the updates to the website that hosts the EOD and the
Exoplanet Data Explorer, exoplanets.org. As one of the mostly visited
exoplanet database, exoplanets.org had $47,000$ visitors in 2013
according to Google Analytics. The Exoplanet Data Explorer has
expanded its scope and now includes the \kepler\ exoplanet
candidates. We describe these changes in Section~\ref{sec:kepler}. The
website has also gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the Website}\label{sec:website}
